---
title: "project"
author: "Clara Mugnai"
date: "3/21/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Making a shiny app - working with data from a git hub repositorydata set, converted to a csv for me to use

```{r}
library(tidyverse)
library (readr)
library(maps)

cities_df <- read_csv("data/uscities.csv")
beer_df <- read_csv("data/beer.csv")
state_df <- ggplot2::map_data("state")

beer_city <- left_join(beer_df, cities_df, by = c("City" = "city")) %>% filter(State == state_id) %>% select(1:11, 17:19)

content <- beer_city %>%
  mutate(popup = paste0('<a href =', beer_city$Name.x, '>',
                        beer_city$Style, '</a>'))


beer_map2 <- leaflet(beer_city) %>%
  setView(lng = -98.583, lat = 39.833, zoom = 4) %>% 
  addTiles() %>% 
  addProviderTiles(providers$Wikimedia) %>% 
  addMarkers(lng = beer_city$lng, lat = beer_city$lat, clusterOptions = markerClusterOptions(), popup = content$popup)

beer_map2

```

Above, I organize the data to have lat and long and use leaflet to make a popup map so you can see the predominant type in each City.
- In the app I want a table to pop up where you can pick a city and see type listed as well, to make it clearer. 

```{r}
library(shiny)
ui <- fluidPage(
  sidebarLayout(sidebarPanel(
    selectizeInput("citychoice",
                   label = "Choose a City", choices = levels(factor(beer_city$City)),
                   selected = "Lincoln"), width = 2),
    mainPanel(leafletOutput("leafplot"),
              tableOutput("citybeer")),
  )
)
server <- function(input, output, session) {
  
   onecity_df <- reactive({beer_city %>% filter(City == input$citychoice) %>% select(3,7,9) %>% rename("Beer name" = "Name.x", "Brewery" = "Name.y")
   })
   
  output$leafplot <- renderLeaflet({
    leaflet(beer_city) %>%
  setView(lng = -98.583, lat = 39.833, zoom = 4) %>% 
  addTiles() %>% 
  addProviderTiles(providers$Wikimedia) %>% 
  addMarkers(lng = beer_city$lng, lat = beer_city$lat, clusterOptions = markerClusterOptions(), popup = content$popup)
  })
  output$citybeer <- renderTable({ onecity_df()
    })
}

shinyApp(ui, server)
```

- Made base shiny app with the front tab as a leaflet with all of the beers and then a table underneath that the person can change for each city. Need to add tabs with styles and plots of the styles.

- Have tabs for both style and brewery - investigate a way to connect the app so you can click on a style or a brewery and be redirected to that tab?