---
title: "Beers and Breweries"
author: "Clara Mugnai"
date: "3/23/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Making a shiny app - working with data from a git hub repositorydata set, converted to a csv for me to use

```{r}
library(tidyverse)
library (readr)
library(maps)
library(leaflet)
library(ggplot2)

cities_df <- read_csv("data/uscities.csv")
beer_df <- read_csv("data/beer.csv")
state_df <- ggplot2::map_data("state")

beer_city <- left_join(beer_df, cities_df, by = c("City" = "city")) %>% filter(State == state_id) %>% select(1:11, 17:19)

content <- beer_city %>%
  mutate(popup = paste0( beer_city$Name.x,"/",
                        beer_city$Name.y))


beer_map2 <- leaflet(beer_city) %>%
  setView(lng = -98.583, lat = 39.833, zoom = 4) %>% 
  addTiles() %>% 
  addProviderTiles(providers$Wikimedia) %>% 
  addMarkers(lng = beer_city$lng, lat = beer_city$lat, clusterOptions = markerClusterOptions(), label = content$popup)

beer_map2

```

Above, I organize the data to have lat and long and use leaflet to make a popup map so you can see the predominant type in each City.

- In the app I want a table to pop up where you can pick a city and see type listed as well, to make it clearer. 

- Made base shiny app with the front tab as a leaflet with all of the beers and then a table underneath that the person can change for each city. Need to add tabs with styles and plots of the styles.

- Have tabs for both style and brewery - investigate a way to connect the app so you can click on a style or a brewery and be redirected to that tab?


Making static plots by style: 
want data set that has mean ABV for each type so that lollipop plot can be made where you pick a style or multiple styles and it shows mean ABV as well as the ABV for each one.
```{r}
style_df <- beer_city %>% group_by(Style) %>%
  summarise(meanABV = mean(ABV, na.rm = TRUE)) %>% 
  ungroup() %>%
  mutate(Style = fct_reorder(Style, meanABV))

ggplot(data = beer_city, aes(x = Style, y = ABV)) +
  geom_point(data = style_df, aes(y = meanABV), color = "Blue", size =2) + 
  geom_point(color = "Red", size = .5) + 
  geom_segment((aes(x=Style, xend=Style, y=0, yend=ABV))) + coord_flip() + labs(x = "Beer Style", y = "ABV content")
```

Want to put this plot into a new tab on the shiny app. Have to figure out how to make a new tab and then put this onto it. -Got the input, need to put in reactive data set.

- look into zooming based on the city you choose - problem! I have ideas to fix this but it is taking forever, something to do with leafletProxy and observe


-Now I will put in reactive lollipop plot because I know how to do that.

- also going to add a lollipop plot that compares IBU values across styles

- this runs so I will change the input of the x so the user can choose either IBU or ABV and they are on the same plot, with the axis label changing conditionally. Next time I work on this. 

- now have title above the table

- Got it to zoom based on input!!

- Added titles for the plots

- Added a descriptive blurb on first tab with text of what the data set is and the app is doing.

- Switched the style tab to a fluid row layout with columns instead of a sidebar sidepanel layout.

Decisions made:

- Change the input of the x so the user can choose either IBU or ABV and they are on the same plot, with the axis label changing conditionally? Could be good to keep both or could be better to have the user choose one. I think I will keep both for the reasoning that it is one less thing for the user to put in and I think the page can handle it.
 - Added a leaflet map that marks on the large scale a dot cluster where each style appears when users picks styles from the style tab.
- Added a tab where user can choose a brewery
- made choices of two brewery options they pick two outputting 
- Made the two table output 
- Made plot output for the breweries and angles labels
- corrected clusters and markers and labels for all of the maps.

Tasks:
  - a map that adjusts zoom to zoom around the two the user picked. currently do not have the two data sets combined.
  - come up with a better way to show the style breakdown.
  - add colors and edit label sizes to make the style and brewery tabs more interesting. 
  - add text outputs above the columns with plots and table what brewery it is showing information for


```{r}
library(shiny)
ui <- fluidPage(
  titlePanel("Breweries and Beers in U.S.A."),
  tabsetPanel(tabPanel("Beer Map", 
    sidebarLayout(sidebarPanel(
      strong("Welcome!", style = "color:forestgreen"),
      p("- This data set is a compiled list of over 2,000 beers from various breweries from around the U.S.A."), 
      p("- Enjoy navigating these tabs in the top left to compare locations, beer styles, and various breweries."), 
      p("- Select inputs from the selections on the left side of the screen and watch the right side change!"), 
      p("- The maps can be zoomed in and out further with mouse scrolling or the +/- buttons, and surprises might appear           if you click your mouse in certain places."),
      p("- Finally, scroll down on the pages to make sure you are not missing any cool content."), 
      p("Enjoy exploring!", style = "color:forestgreen"),
    selectizeInput("citychoice",
                   label = "Choose a City", choices = levels(factor(beer_city$City)),
                   selected = "Austin"), width = 3),
    mainPanel(leafletOutput("leafplot"),
              span(textOutput("tabletitle"), style = "font-size:150%"),
              tableOutput("citybeer")),
   )
  ),
 tabPanel("Styles",
          fluidRow(
            column(selectizeInput("stylechoice",
                           label = "Choose a Style", choice = levels(factor(beer_city$Style)),
                           selected = "Belgian IPA", multiple = TRUE), width = 2),
            column(6,
                    plotOutput("lollipop1"),
                   plotOutput("lollipop2")),
            column(4,
                    leafletOutput("leafplot2")),
      )),
 tabPanel("Breweries",
          fluidRow(
            column(selectizeInput("brewerychoice",
                           label = "Choose a Brewery", choice = levels(factor(beer_city$Name.y)),
                           selected = "NorthGate Brewing"),
                   selectizeInput("brewerychoice2",
                            label = "Choose another Brewery", choice = levels(factor(beer_city$Name.y)),
                            selected = "Avery Brewing Company"), width = 2),
            column(4,
                   plotOutput("histogram1"),
                   tableOutput("brewery1")),
            column(4,
                   plotOutput("histogram2"),
                   tableOutput("brewery2")),
            column(2,
                   leafletOutput("leafplot3")),
          ))
  ))
server <- function(input, output, session) {
  
   onecity_df <- reactive({beer_city %>% filter(City == input$citychoice) %>% rename("Beer name" = "Name.x", "Brewery" = "Name.y")
   })
   style <- reactive({beer_city %>% filter(Style %in% input$stylechoice)
     })
   style2 <- reactive({beer_city %>% filter(Style %in% input$stylechoice)%>% group_by(Style) %>%
  summarise(meanABV = mean(ABV, na.rm = TRUE)) %>% 
  ungroup() %>%
  mutate(Style = fct_reorder(Style, meanABV))
     })
   style3 <- reactive({beer_city %>% filter(Style %in% input$stylechoice)%>% group_by(Style) %>%
  summarise(meanIBU = mean(IBU, na.rm = TRUE)) %>% 
  ungroup() %>%
  mutate(Style = fct_reorder(Style, meanIBU))
     })
   onebrewery_df <- reactive({beer_city %>% filter(Name.y == input$brewerychoice) %>% rename("Beer name" = "Name.x", "Brewery" = "Name.y")
   })
   onebrewery_df2 <- reactive({beer_city %>% filter(Name.y == input$brewerychoice2) %>% rename("Beer name" = "Name.x", "Brewery" = "Name.y")
   })
   
  output$leafplot <- renderLeaflet({
    leaflet(beer_city) %>%
  flyTo(lng = -98.583, lat = 39.833, zoom = 6) %>% 
  addTiles() %>% 
  addProviderTiles(providers$Wikimedia) %>% 
  addMarkers(lng = beer_city$lng, lat = beer_city$lat, clusterOptions = markerClusterOptions(), label = content$popup)
  })
  
   observe({
    city <- onecity_df()
    leafletProxy("leafplot") %>% fitBounds(min(city$lng), min(city$lat),
                                        max(city$lng+1/4), max(city$lat+1/4))
  })
  
  output$tabletitle <- renderText({
    (input$citychoice)
  })
  
  output$citybeer <- renderTable({ 
    onecity_df() %>% select(3,7,9)
    })
  
  output$lollipop1 <- renderPlot({
    ggplot(data = style(), aes(x = Style, y = ABV)) +
  geom_point(data = style2(), aes(y = meanABV), color = "Blue", size = 3) + 
  geom_point(color = "Red", size = 2) + 
  geom_segment((aes(x=Style, xend=Style, y=0, yend=ABV))) + coord_flip() + labs(x = "Beer Style", y = "ABV content", title = "Average ABV content by Beer Style")
  })
  
  output$lollipop2 <- renderPlot({
    ggplot(data = style(), aes(x = Style, y = IBU)) +
  geom_point(data = style3(), aes(y = meanIBU), color = "Blue", size = 3) + 
  geom_point(color = "Red", size = 2) + 
  geom_segment((aes(x=Style, xend=Style, y=0, yend=IBU))) + coord_flip() + labs(x = "Beer Style", y = "IBU content", title = "Average IBU content by Beer Style")
  })
  
  output$leafplot2 <- renderLeaflet({
    leaflet(beer_city) %>%
  flyTo(lng = -98.583, lat = 39.833, zoom = 3) %>% 
  addTiles() %>% 
  addProviderTiles(providers$Wikimedia)
  })
  
  observe({
    style <- style()
    leafletProxy("leafplot2") %>% clearMarkerClusters() %>% addMarkers(lng = style$lng, lat = style$lat, label = paste0( style$Name.x,"/", style$Style), clusterOptions = markerClusterOptions())
    
  })
  
  output$histogram1 <- renderPlot({
    ggplot(data = onebrewery_df() %>% group_by(Style), aes(x = Style)) + 
      geom_bar() + labs(x = "Style", y = "Beer Number", title = "Beer Style Breakdown") + theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1))
                                                                                                
  })
  
  output$brewery1 <- renderTable({
    onebrewery_df() %>% select(3,7,9)
  })
  
  output$histogram2 <- renderPlot({
    ggplot(data = onebrewery_df2() %>% group_by(Style), aes(x = Style)) + 
      geom_bar() + labs(x = "Style", y = "Beer Number", title = "Beer Style Breakdown") + theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1))
    
  })
  
  output$brewery2 <- renderTable({
    onebrewery_df2() %>% select(3,7,9)
  })
  
  output$leafplot3 <- renderLeaflet({
    leaflet(beer_city) %>%
  flyTo(lng = -98.583, lat = 39.833, zoom = 3) %>% 
  addTiles() %>% 
  addProviderTiles(providers$Wikimedia)
  })
  
  observe({
    brewery <- onebrewery_df()
    leafletProxy("leafplot3") %>% clearMarkerClusters() %>% fitBounds(min(brewery$lng), min(brewery$lat),
                                        max(brewery$lng-2), max(brewery$lat-2)) %>% addMarkers(lng = brewery$lng, lat = brewery$lat, clusterOptions = markerClusterOptions(), label = paste0( brewery$`Beer name`,"/", brewery$Brewery))
  })
}
shinyApp(ui, server)
```
